On particular examples of planar integral point sets and their classification \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2021-03-15 AvdMomZvolA_examples/ips_examples.tex
[AMZAE] Fixes before arXiv

\begin{figure}[h!]
\center{\includegraphics[width=1\linewidth]{./img/15_61960444_1_other.png}}
\parbox{1\linewidth}{\caption{IPS of cardinality 15 and diameter 61960444}
\label{15_61960444_1.png}}
\end{figure}

\begin{figure}[h!]
\center{\includegraphics[width=1\linewidth]{./img/15_45970652_1_other.png}}
\parbox{1\linewidth}{\caption{IPS of cardinality 15 and diameter 45970652}
\label{15_45970652_1.png}}
\end{figure}

\begin{itemize}
\item
$\mathcal{P}=\sqrt{1}/1*\{
( \pm9406950 ; 0);
( \pm7063350 ; 0);
( 2962050 ; \pm3437280);
( 0 ; 0);
( -2962050 ; \pm3437280);\\
( \pm2188662 ; 0);
( \pm30980222 ; 0);
( \pm2914854 ; 0);
\}$

\item
$\mathcal{P}=\sqrt{1}/1*\{
( \pm6979350 ; 0);
( \pm5240550 ; 0);
( 2197650 ; \pm2550240);
( 0 ; 0);
( -2197650 ; \pm2550240);\\
( \pm1623846 ; 0);
( \pm22985326 ; 0);
( \pm2476152 ; 0);
\}$
\end{itemize}

%TODO: 11_14450_1_8693fad981c82dc92d7c9365bcb9945e

%The set on Fig. TODO has been obtained from the set on Fig. TODO by dilation by 5.

%The set on Fig. TODO has been obtained from the set on Fig. TODO by dilation by 42 (or less? TODO).

\section{Arrow-like integral point sets with one axis of symmetry}

Figure~\ref{17_1024296_1_639b}:
\begin{multline}
	\mathcal{P}_8=
	\sqrt{1}/1*\{
		( -2847 ; \pm72072);
		( 47073 ; \pm124488);
		( 47073 ; 0);
		( \pm98943 ; 0);
		\\
		( -71487 ; 0);
		( -694668 ; 0);
		( 15457 ; 0);
		( 23582 ; 0);
		( 125307 ; 0);
		\\
		( 329628 ; 0);
		( -50367 ; 0);
		( -14943 ; 0);
		( 63073 ; 0);
		( 172207 ; 0)
	\}
\end{multline}

>>>>

The set $\mathcal{P}_{19}$ shown on Figure~\ref{19_41327616148} was obtained from the set shown on Figure~\ref{9_2890_1_02e6af}
by dilation and looking for points on $x$ axis.

\begin{figure}[h!]
\center{\includegraphics[width=1\linewidth]{./img/9_2890_1_02e6afb1c19846c6c4debb44e52cc468_other.png}}
\parbox{1\linewidth}{\caption{IPS of cardinality 9 and diameter 2890}
\label{9_2890_1_02e6af}}
\end{figure}

\begin{equation}
	\mathcal{P}_9=\sqrt{1}/1*\{
	( 0 ; 0);
	( \pm1445 ; 0);
	( \pm1085 ; 0);
	( -455 ; \pm528);
	( 455 ; \pm528)
	\}
\end{equation}

\begin{figure}[h!]
\center{\includegraphics[width=1\linewidth]{./img/19_41327616148_1_88f7a023e19224a633e4213ec953bd8d_other.png}}
\parbox{1\linewidth}{\caption{IPS of cardinality 19 and diameter 41327616148}
\label{19_41327616148}}
\end{figure}

\begin{multline}
	\mathcal{P}_{19}=
	\sqrt{1}/1*\{(
	\pm5492845050 ; 0);
	( 1194096750 ; \pm2292665760);
	( -2757277950 ; \pm2292665760);
	\\
	( 3929663850 ; 0);
	( -781590600 ; 0);
	( -7056026250 ; 0);
	( -2241428154 ; 0);
	\\
	( 678246954 ; 0);
	( -21445398674 ; 0);
	( 19882217474 ; 0);
	( -2725798218 ; 0);
	\\
	( 1162617018 ; 0);
	( -3007651248 ; 0);
	( 1444470048 ; 0);
	( -3581930898 ; 0);
	( 2018749698 ; 0)
\}
\end{multline}

\section{Arrow-like integral point set with one axis of symmetry}

Figure~\ref{17_1024296_1_639b}:
\begin{multline}
	\mathcal{P}_{17}=
	\sqrt{1}/1*\{
		( -2847 ; \pm72072);
		( 47073 ; \pm124488);
		( 47073 ; 0);
		( \pm98943 ; 0);
		\\
		( -71487 ; 0);
		( -694668 ; 0);
		( 15457 ; 0);
		( 23582 ; 0);
		( 125307 ; 0);
		\\
		( 329628 ; 0);
		( -50367 ; 0);
		( -14943 ; 0);
		( 63073 ; 0);
		( 172207 ; 0)
	\}
\end{multline}
